A Triple Origin for Twin Blue Stragglers in Compact Binaries

### 2018-12-19 BSS7782.tex
started working on the text

We propose a formation mechanism for twin blue stragglers in compact
binaries that involves mass transfer from an evolved outer tertiary
companion on to the inner binary via a circumbinary disk.  We apply
our hypothetical scenario to the observed double blue straggler system
Binary 7782 in the old open cluster NGC 188, and show that its
observed properties are naturally reproduced within the context our
proposed model.  Within the context of the hypothetical formation
mechanism proposed here, the presented work predicts the following
properties for the post-mass transfer double BS tertiary: (1) For the
outer tertiary orbit, the initial orbital period should lie between
220 days $\lesssim$ P$_{\rm out}$ $\lesssim$ 1100 days, assuming
initial masses for the inner binary components of m$_{\rm 1} =$ 1.1
M$_{\odot}$ and m$_{\rm 2} =$ 0.9 M$_{\odot}$ and an outer tertiary
mass of m$_{\rm 3} =$ 1.4 M$_{\odot}$. (2) Larger final WD masses, and
hence core masses for the donor at the time of mass transfer, should
correspond to larger final outer orbital periods for the tertiary. (3)
For the inner binary, the rotational axes of the BSs should be aligned
with each other and the orbital plane of the outer tertiary WD. (4)
The BSs in the inner binary should have roughly equal masses,
independent of their initial masses.  This predicts that the initially
lower mass MS star should accrete the most, and should hence be
polluted more effectively by the accreted material.  This could be
observable in the surface layers of a radiative star (i.e., He, C and
O if the donor is an RGB star, and/or s-process elements if the donor
is an AGB star). (5) Twin BSs in compact binaries formed from the
proposed mechanism should be more frequent in younger clusters with
ages $\lesssim$ 4-6 Gyr, since the donor will have a radiative envelope.

@@

Blue straggler (BS) stars are brighter and bluer than the
main-sequence turn-off (MSTO) in a cluster colour-magnitude diagram
(CMD) \citep[e.g.][]{1953AJ.....58...61S,simunovic14,simunovic16}.
Two primary channels for BS formation have been proposed; mass
transfer from an evolved donor on to a main-sequence star in a binary
star system
\citep[e.g.][]{mccrea64,997A&A...328..143P,knigge09,mathieu09,leigh11,geller11,geller12,gosnell14,gosnell15},
and direct stellar collisions involving main-sequence stars mediated
via direct interactions involving binaries
\citep[e.g.][]{hills75,1997A&A...328..130P,shara97,leigh07,leigh11,leigh13,hypki13,2018arXiv181100058P}.
Other possible, albeit related, formation mechanisms include mergers
of compact main-sequence binaries (ms, ms), and mergers of the inner
binaries of hierarchical triple star systems induced by Lidov-Kozai
oscillations coupled with tidal damping \citep[e.g.][]{perets09}.

In spite of these specific predictions for the expected properties of
BSs formed from each of the above production mechanisms, there exist
many BSs with observed properties that defy these simple scenarios.
\del{For example, in the old open cluster M67, there lurks a candidate
  triple system that is posited to host \textit{two} BSs
  \citep{vandenberg01,sandquist03}.  The observations suggest that the
  outer tertiary is itself a BS, with a mass $\sim$ 1.7 M$_{\odot}$
  and orbiting the inner binary with a period of 1188.5 days
  \citep{sandquist03}.  The inner binary has a period of only 1.068
  days \citep{vandenberg01}, and hosts a BS of mass 2.52 M$_{\odot}$.}
In order to form this system after convolving its observed properties
with its host cluster age, we require at least five stars in order to
conserve the total system mass \citep{leigh11}.  As explained in
\citet{leigh11}, this is strongly indicative of a dynamical origin for
the system, and a single direct interaction involving a binary and a
triple that resulted in two separate collision events is the most
probable explanation for its origin (i.e., a single interaction
involving two multiples with two or more stars is a more likely
scenario to produce this system than two back-to-back direct
binary-binary interactions) \citep{2004MNRAS.350..615G}.

Even more curious, there exists in the old open cluster NGC 188 a
double BS binary, called Binary 7782.  More generally, the BS population in NGC 188 has a bi-modal period-eccentricity distribution.  As discussed in \citet{leigh11}, this could be hinting at a triple origin for at least some subset of the total BS population.  As for Binary 7782, \citet{mathieu09}
observed a compact and mildly eccentric (i.e., e $\sim$ 0.1) binary
star system with an orbital period of $\sim$ 10 days hosting two roughly equal-mass blue
stragglers.  During a given binary-binary interaction, the probability
that not one but two direct (ms, ms) collisions occur is less than
$10^{-2}$ \citep{leonard89,leigh11,leigh12}.  Typically, such binaries
have long orbital periods. Dynamically, it is difficult to form a
short-period binary composed of two collision products during a
collision interaction in a star cluster \citep{2011Sci...334.1380F}.
So, how did Binary 7782 form?

We propose a formation channel for Binary 7782, and compact double BS
binaries in general, which involves mass transfer from an outer
tertiary companion on to an inner MS-MS binary.  In section~\ref{dyn},
we constrain the range of initial (i.e., pre-mass transfer) orbital
parameters for a hypothetical outer tertiary companion, using a
combination of dynamical and stellar evolution-based constraints.  In
Section~\ref{sims} we present the numerical simulations used to study
the mass transfer process in our hypothetical triple system, computed
using the \texttt{AMUSE}\cite{AMUSE} software package, in order to
study the evolution of the inner and outer orbital parameters during
mass transfer.  We summarize and discuss the implications of our
results for compact double BS binaries and, more generally, mass
transfer in stellar triples in Section~\ref{discussion}.

@@

Consider a hierarchical triple system with component masses m$_{\rm
  1}$ and m$_{\rm 2}$ for the inner binary, and mass m$_{\rm 3}$ for
the outer tertiary companion.  The inner and outer binary orbital
semi-major axes are denoted a$_{\rm in}$ and a$_{\rm out}$,
respectively.  We assume circular orbits for both the inner and outer
orbits, and co-planar triples only since this is what has been
observed for low-mass tertiaries \cite{2010yCat..73890925T,moe18} \simon{I
  think that {\em moe18} and {\em tobin18} are not the right
  references - NL: I checked and I think the moe18 reference, at least, is fine, so I added it back in.  But feel free to remove it, if you prefer.}.  This initial configuration for our assumed formation
scenario for Binary 7782, described below, is depicted in
Figure~\ref{fig:fig1}.

\begin{figure}[ht!]
\plotone{fig1.eps}
\caption{Cartoon depiction of our proposed scenario for the formation
  of Binary 7782, specifically mass transfer from an evolved outer
  tertiary companion on to a compact inner binary via a circumbinary
  disk.  The outer tertiary component has mass m$_{\rm 3}$, whereas
  the inner binary components have masses m$_{\rm 1}$ and m$_{\rm 2}$.
  The inner and outer orbital separations are denoted by,
  respectively, a$_{\rm in}$ and a$_{\rm out}$.  The circularization
  radius of the accretion stream is denoted a$_{\rm c}$, as calculated
  via Equation~\ref{eqn:ac}, and marks the mean separation of the
  circumbinary disk.
\label{fig:fig1}}
\end{figure}

We consider a scenario where the outer star is filling its Roche lobe
and transfers mass to the inner binary.  The mass transfer stream
gathers at the circularization radius a$_{\rm c}$, and forms a disk
around the inner binary.  Using conservation of angular momentum, we
equate the specific angular momentum of the accreted mass at the inner
Lagrangian point of the (outer) donor star to the final specific
angular momentum of the accretion stream at the circularization radius
about the inner binary, this results in
\simon{replaced lower case $r$ with upper case.}
\begin{equation}
\label{eqn:specangmom1}
v_{\rm orb,3}(a_{\rm out} - R_{\rm L}) = v_{\rm orb,c}a_{\rm c},
\end{equation}
where R$_{\rm L}$ is the radius of the Roche lobe of the outer
tertiary companion, a$_{\rm c}$ is the semi-major axis of the orbit
about the inner binary corresponding to the circularization radius and
v$_{\rm orb,c}$ is the orbital velocity at a$_{\rm c}$.  The distance
from the center of mass corresponding to the outer tertiary companion
defined by the Roche lobe is given by Equation 2 in \citep{eggleton83}.
\simon{Do we really need this eq? - NL: Good call, no.  We can definitely remove this to save space, given that this is a Letter.  I have done so.}
%\begin{equation}
%\label{eqn:roche}
%R_{\rm L} = \frac{0.49q^{2/3}}{0.6q^{2/3} + {\rm ln}(1 + q^{1/3})}a_{\rm out},
%\end{equation}
%where the mass ratio q is defined as q $=$ m$_{\rm 3}$/(m$_{\rm 1} +$
%m$_{\rm 2}$).  
Combining Equation 2 in \citet{eggleton83} (with mass ratio q $=$ m$_{\rm 3}$/(m$_{\rm 1} +$m$_{\rm 2}$)) with
Equation~\ref{eqn:specangmom1}, we can solve for the circularization
radius as a function of a$_{\rm out}$ and the assumed stellar masses:
\begin{equation}
\label{eqn:ac}
a_{\rm c} = a_{\rm out}(1 - R_{\rm L}).
\end{equation}
In order for a circumbinary disk to form around the inner binary, we
require that a$_{\rm in} <$ a$_{\rm c}$.

Figure~\ref{fig:fig2} shows the parameter space in the P$_{\rm
  out}$-P$_{\rm in}$-plane for Binary 7782.  We assume initial
component masses of m$_{\rm 1} =$ 1.1 M$_{\rm \odot}$ and m$_{\rm 2}
=$ 0.9 M$_{\rm \odot}$ for the inner binary components, and m$_{\rm 3}
=$ 1.4 M$_{\rm \odot}$ for the outer tertiary.  We compare the
circularization radius to the semi-major axis of the inner binary, for
which we require a$_{\rm c} >$ a$_{\rm in}$, \del{after folding in all
  constraints from the requirements for dynamical stability (listed in the caption of Figure~\ref{fig:fig2})}\simon{can
  we not simply state the constraints? - We do, but it is in the caption to save space.  It is all there anyways, so can be brought in to the main text if necessary.}, an outer tertiary that is
Roche lobe-filling, and a dynamically hard outer tertiary orbit.  Note
that the range of plotted orbital periods P$_{\rm in}$ corresponding
to a contact state for the inner binary lies outside the
range of plotted values for P$_{\rm in}$ (for components with radii of roughly 1 R$_{\odot}$), since it does not contribute
significantly to constraining the outer orbital properties of a
hypothesized outer WD tertiary.  The thick horizontal solid red line
shows the allowed range of outer semi-major axes, after folding in all
of the aforementioned criteria.  As is clear, this makes a relatively
narrow prediction for the allowed ranges of outer tertiary orbits,
namely 2.2 $\times$ 10$^{2}$ days $\le$ P$_{\rm out}$ $\le$ 1.1
$\times$ 10$^3$ days, for our assumed final donor mass.

@@

RLOF in triples is modeled using a coupled integrator to follow the complex
hydrodynamics of the mass transfer from the Roche-lobe filling outer
star to the inner binary, while keeping track of the gravitational
dynamics of the stars.  The equations of motion of the inner binary are 
solved using the semi-symplectic direct N-body integrator
\texttt{Huayno} \citep{2012NewA...17..711P}. The hydrodynamics is
performed with the smoothed-particles hydrodynamics code
\texttt{Gadget2} \citep{2000ascl.soft03001S}, using an adiabatic
equation of state.  The two inner binary stars are treated as point
masses, but we allow them to accrete gas from the outer star.  This is
realized using sink-particles that co-move with the mass points in the
gravity code. While the inner two stars accrete mass, they also
accrete the corresponding amount of angular momentum from the gas.  
The the N-body integrator accounts of this appropriately.  For the
radius of the sink particles we adopt $10 R_\odot$ for both stars.

The N-body code as well as the hydrodynamics solver operate using
their own internal time-steps. The coupling between the two codes is
realized using the \texttt{Bridge} method in the AMUSE framework
\citep[see Sect.\.4.3.1 in][]{2013CoPhC.183..456P}.  This coupled
integrator is based on the splitting of the Hamiltonian, much in the
same way as is done with two different gravity solvers by
\cite{2007PASJ...59.1095F}. With the adopted scheme, the
hydrodynamical solver is affected by the gravitational potential of
its own particles, as well as the gravitational potential of the inner
binary. The hydrodynamics, in particular the gas drag, in turn affects
the orbits of the two inner stars. With \texttt{Bridge} we realize a
second order coupling between the gravitational dynamics and the
hydrodynamics.  The interval at which the gravity and hydrodynamics
interact via \texttt{Bridge} depends on the parameters of the system
we study, but typically we achieve converged solutions when this time
step is about a fraction of 1/100 of the inner binary orbital period.

@@

We adopt initial component masses of m$_{\rm 1}$ = 1.1 M$_{\rm \odot}$
and m$_{\rm 2}$ = 0.9 M$_{\rm \odot}$ for the inner binary components,
and m$_{\rm 3}$ = 1.2 M$_{\rm \odot}$ for the tertiary star.  We
evolve the 1.2\,\MSun\, star using the MESA stellar evolution code
\cite{2011ApJS..192....3P} to a radius of about 255\,\RSun.  By this
time the star has lost 0.13\,\MSun\, via a stellar wind.  With these
parameters the orbital separation of the outer binary becomes 3.86\,au,
and the mass loss has driven a slight eccentricity deviating from an initially
circular orbit to about 0.0082 at the moment of Roche-lobe
overflow. We choose a relative initial inclination of $i = 9^\circ$
between the inner and the outer orbits, since observed stellar triples composed of low-mass stars have been observed to favor co-planar configurations \citep{moe18}.
%NL: What are the initial orbital separations?  Why this choice of initial inclination? - I added a sentence and reference to justify it.

@@

\begin{figure}[ht!]
  \includegraphics[width=\columnwidth]{fig_MvsTime_N80k_M012R100RSun1109MSun_a02au.pdf}
\caption{Evolution of the masses (normalized to those at the moment of
  Roche-lobe overflow) for each of the three stars in the simulated triple as a function of
  time for the first 1000\,days. (see fig.\,\ref{fig:topview_at_t0}
  for a face-on representation of the initial conditions and
  fig.\,\ref{fig:topview_at_t1000day} for the final conditions}.  The
green and orange dashed curves give the masses of the inner two stars,
whereas the solid blue curve is the mass of the outer most star.
\label{fig:mass_evolution_for_M1.2M1.1M0.9a02e00i09}
\end{figure}

@@

\item The BSs in the inner binary should have roughly equal masses, independent of their initial masses.  This is because it is the lowest mass object that typically accretes the fastest, since its orbital velocity and distance relative to the circumbinary disk is typically the lowest \citep[e.g.][]{kroupa95,bate97,bate00,haiman09,bate12,farris15,rafikov16,kelley17}.  This quickly brings the mass ratio toward unity.  This predicts that the initially lower mass MS star should accrete the most, and should hence be polluted more significantly by any accreted material.  This could be observable in the surface layers of a radiative star.  If the donor is an RGB star, the accretor will be enriched in mostly carbon, oxygen and helium.  If the donor is an AGB star, it will be enriched in mostly s-process elements.

>>>>

We propose a formation mechanism for twin blue stragglers in compact
binaries that involves mass transfer from an evolved outer tertiary
companion on to the inner binary via a circumbinary disk.  We apply
our scenario to the observed double blue straggler system Binary 7782
in the old open cluster NGC 188, and show that its observed properties
are naturally reproduced within the context our proposed model.
Within the context of the hypothetical formation mechanism proposed
here, the presented work predicts the following properties for the
post-mass transfer double BS tertiary: (1) For the outer tertiary
orbit, the initial orbital period should lie between 220 days
$\lesssim$ P$_{\rm out}$ $\lesssim$ 1100 days \simon{Do you think that
  the initial binary could be as large as 1400 days?}, assuming
initial masses for the inner binary components of m$_{\rm 1} =$ 1.1
M$_{\odot}$ and m$_{\rm 2} =$ 0.9 M$_{\odot}$ and an outer tertiary
mass of m$_{\rm 3} = 1.4$ M$_{\odot}$.  After Roche-lobe overflow, the
outer star turns into a white dwarf (WD). There is a correlation
bewteen the mass of this WD and the outer orbital period in the sense
that a more massive white dwarfs will be on a wider orbit.  (3) The
rotational axes of the BSs in the inner binary should be aligned with
each other and the orbital plane of the outer tertiary WD. (4) The BSs
in the inner binary should have roughly equal masses, independent of
their initial masses.  This predicts that the initially lower mass MS
star should accrete the most, and should hence be enriched more
effectively by the accreted material.  This could be observable in the
surface layers of a radiative star (i.e., He, C and O enrichment if
the donor is an RGB star, and/or s-process elements if the donor is an
AGB star). (5) Twin BSs in compact binaries formed from the proposed
mechanism should be more frequent in younger clusters \simon{WHy not
  in the field?} with ages $\lesssim$ 4-6 Gyr, since the donor will
have a radiative envelope. (6) the orbital of the binary BS will be
tight (typically $\aplt 0.3$\,au) and close to circular ($e \aplt
0.2$).

@@

Blue straggler (BS) stars are brighter and bluer than the
main-sequence turn-off (MSTO) in a cluster colour-magnitude diagram
\citep[e.g.][]{1953AJ.....58...61S,simunovic14,simunovic16}.  Two
primary channels for BS formation have been proposed; mass transfer
from an evolved donor on to a main-sequence star in a binary star
system
\citep[e.g.][]{mccrea64,997A&A...328..143P,knigge09,mathieu09,leigh11,geller11,geller12,gosnell14,gosnell15},
and direct stellar collisions involving main-sequence stars possibly
mediated via binaries
\citep[e.g.][]{hills75,1997A&A...328..130P,shara97,leigh07,leigh11,leigh13,hypki13,2018arXiv181100058P}.
Other possible, albeit related, formation mechanisms include mergers
of compact main-sequence binaries (ms, ms), and mergers of the inner
binaries \cite{+++} of hierarchical triple star systems induced by Lidov-Kozai
oscillations coupled with tidal damping \citep[e.g.][]{perets09}.

In spite of these specific predictions for the expected properties of
BSs formed from each of the above production mechanisms, there exist
many BSs with observed properties that defy these simple scenarios.
For example, in the old open cluster M67, there lurks a candidate
triple system that is posited to host two BSs
\citep{vandenberg01,sandquist03}.  The observations suggest that the
outer tertiary is itself a BS, with a mass $\sim$ 1.7 M$_{\odot}$ and
orbiting the inner binary with a period of 1188.5 days
\citep{sandquist03}.  The inner binary has a period of only 1.068 days
\citep{vandenberg01}, and hosts a BS of mass 2.52 M$_{\odot}$.  In
order to form this system \del{after convolving its observed
  properties with its host cluster age,} we require at least five
stars in order to conserve the total system mass \citep{leigh11}.  As
explained in \citet{leigh11}, this is strongly indicative of a
dynamical origin for the system, and a single direct interaction
involving a binary and a triple that resulted in two separate
collision events is the most probable explanation for its origin
(i.e., a single interaction involving two multiples with two or more
stars is a more likely scenario to produce this system than two
back-to-back direct binary-binary interactions)
\citep{2004MNRAS.350..615G}.  \simon{Maybe add something about the
  curious binary AE Aurigae?}

Even more curious, there exists in the old open cluster NGC 188 a
double BS binary, called Binary 7782.  More generally, the BS
population in NGC 188 has a bi-modal period-eccentricity distribution.
As discussed in \citet{leigh11}, this could be hinting at a triple
origin for at least some subset of the total BS population.  As for
Binary 7782, \citet{mathieu09} observed a compact and mildly eccentric
(i.e., $e \sim 0.1$) binary star system with an orbital period of
$\sim$ 10 days hosting two roughly equal-mass blue stragglers.  During
a given binary-binary interaction, the probability that not one but
two direct (ms, ms) collisions occur is less than $10^{-2}$
\citep{leonard89,leigh11,leigh12}.  Binaries with collision products
typically have relatively long orbital periods
\cite{2011Sci...334.1380F}. Dynamically, it is difficult to form a
short-period binary composed of two collision products during a
collision interaction in a star cluster \citep{2011Sci...334.1380F}.
So, how did Binary 7782 form?

We propose a formation channel for Binary 7782, and compact double BS
binaries in general, which involves mass transfer from an outer
tertiary companion on to an inner (ms, ms) binary.  In
section~\ref{dyn}, we constrain the range of initial (i.e., pre-mass
transfer) orbital parameters for a hypothetical outer tertiary
companion, using a combination of dynamical and stellar
evolution-based constraints.  In Section~\ref{sims} we present the
numerical simulations used to study the mass transfer process in our
hypothetical triple system, computed using the
\texttt{AMUSE}\cite{AMUSE} software package, in order to study the
evolution of the inner and outer orbital parameters during mass
transfer.  We summarize and discuss the implications of our results
for compact double BS binaries and, more generally, mass transfer in
stellar triples in Section~\ref{discussion}.

@@

Consider a hierarchical triple system with component masses m$_{\rm
  1}$ and m$_{\rm 2}$ for the inner binary, and mass m$_{\rm 3}$ for
the outer tertiary companion.  The inner and outer binary orbital
semi-major axes are denoted a$_{\rm in}$ and a$_{\rm out}$,
respectively.  For clarity we now assume both orbits, the inner as
well as the outer to have a small eccentricity and low inclination.
These assumptions are also supported by the population of observed
low-mass triples \cite{2010yCat..73890925T,moe18}.  This initial
configuration for our assumed formation scenario for Binary 7782,
described below, is depicted in Figure~\ref{fig:fig1}.

\begin{figure}[ht!]
\plotone{fig1.eps}
\caption{Cartoon depiction of our proposed scenario for the formation
  of Binary 7782, specifically mass transfer from an evolved outer
  tertiary companion on to a compact inner binary via a circumbinary
  disk.  The outer tertiary component has mass m$_{\rm 3}$, whereas
  the inner binary components have masses m$_{\rm 1}$ and m$_{\rm 2}$.
  The inner and outer orbital separations are denoted by,
  respectively, a$_{\rm in}$ and a$_{\rm out}$.  The circularization
  radius of the accretion stream is denoted a$_{\rm c}$, as calculated
  via Equation~\ref{eqn:ac}, and marks the mean separation of the
  circumbinary disk.\
  \simon{Should we also indicate the accretion stream onto the two stars?}
\label{fig:fig1}}
\end{figure}

We consider a scenario where the outer star is filling its Roche lobe
and transfers mass to the inner binary.  The mass transfer stream
gathers at the circularization radius a$_{\rm c}$, and forms a disk
around the inner binary.  Using conservation of angular momentum, we
equate the specific angular momentum of the accreted mass at the inner
Lagrangian point of the (outer) donor star to the final specific
angular momentum of the accretion stream at the circularization radius
about the inner binary, this results in
\begin{equation}
\label{eqn:specangmom1}
v_{\rm orb,3}(a_{\rm out} - R_{\rm L}) = v_{\rm orb,c}a_{\rm c},
\end{equation}
where R$_{\rm L}$ is the radius of the Roche lobe of the outer
tertiary companion, $a_{\rm c}$ is the semi-major axis of the orbit
about the inner binary corresponding to the circularization radius and
v$_{\rm orb,c}$ is the orbital velocity at $a_{\rm c}$.  The distance
from the center of mass corresponding to the outer tertiary companion
defined by the Roche lobe is given by Equation 2 in \citep{eggleton83}.
%\begin{equation}
%\label{eqn:roche}
%R_{\rm L} = \frac{0.49q^{2/3}}{0.6q^{2/3} + {\rm ln}(1 + q^{1/3})}a_{\rm out},
%\end{equation}
%where the mass ratio q is defined as q $=$ m$_{\rm 3}$/(m$_{\rm 1} +$
%m$_{\rm 2}$).  
Combining Equation 2 in \citet{eggleton83} (with mass ratio q $=$ m$_{\rm 3}$/(m$_{\rm 1} +$m$_{\rm 2}$)) with
Equation~\ref{eqn:specangmom1}, we can solve for the circularization
radius as a function of a$_{\rm out}$ and the assumed stellar masses:
\begin{equation}
\label{eqn:ac}
a_{\rm c} = a_{\rm out}(1 - R_{\rm L}).
\end{equation}
In order for a circumbinary disk to form around the inner binary, we
require that a$_{\rm in} <$ a$_{\rm c}$.

Figure~\ref{fig:fig2} shows the parameter space in the P$_{\rm
  out}$-P$_{\rm in}$-plane for Binary 7782.  We assume initial
component masses of $m_{\rm 1} = 1.1$ M$_{\rm \odot}$ and $m_{\rm 2}
= 0.9$ M$_{\rm \odot}$ for the inner binary components, and $m_{\rm 3}
= 1.4 M$_{\rm \odot}$ for the outer tertiary.  We compare the
circularization radius to the semi-major axis of the inner binary, for
which we require $a_{\rm c} > a_{\rm in}$, after folding in all
constraints from the requirements for dynamical stability (listed in
the caption of Figure~\ref{fig:fig2}), an outer tertiary that is Roche
lobe-filling, and a dynamically hard outer tertiary orbit.  Note that
the range of plotted orbital periods P$_{\rm in}$ corresponding to a
contact state for the inner binary lies outside the range of plotted
values for $P_{\rm in}$ (for components with radii of roughly 1
R$_{\odot}$), since it does not contribute significantly to
constraining the outer orbital properties of a hypothesized outer WD
tertiary.  The thick horizontal solid red line shows the allowed range
of outer semi-major axes, after folding in all of the aforementioned
criteria.  As is clear, this makes a relatively narrow prediction for
the allowed ranges of outer tertiary orbits, namely 2.2 $\times$
10$^{2}$ days $\le$ P$_{\rm out}$ $\le$ 1.1 $\times$ 10$^3$ days, for
our assumed final donor mass.

@@

Roche-lobe overflow in triples is modeled using a coupled integrator
to follow the complex hydrodynamics of the mass transfer from the
Roche-lobe filling outer star to the inner binary, while keeping track
of the gravitational dynamics of the stars.  The equations of motion
of the inner binary are solved using the symplectic direct N-body
integrator \texttt{Huayno} \citep{2012NewA...17..711P}. The
hydrodynamics is performed with the smoothed-particles hydrodynamics
code \texttt{Gadget2} \citep{2000ascl.soft03001S}, using an adiabatic
equation of state.  The two inner binary stars are treated as point
masses, but we allow them to accrete gas from the outer star.  This is
realized using sink-particles that co-move with the mass points in the
gravity code. While the inner two stars accrete mass, they also
accrete the corresponding amount of angular momentum from the gas.
The the N-body integrator accounts of this appropriately.  For the
radius of the sink particles we adopt $2 R_\odot$ for both stars.

The N-body code as well as the hydrodynamics solver operate using
their own internal time-steps. The coupling between the two codes is
realized using the \texttt{Bridge} method in the AMUSE framework
\citep[see Sect.\.4.3.1 in][]{2013CoPhC.183..456P}.  This coupled
integrator is based on the splitting of the Hamiltonian, much in the
same way as is done with two different gravity solvers by
\cite{2007PASJ...59.1095F}. With the adopted scheme, the
hydrodynamical solver is affected by the gravitational potential of
its own particles, as well as the gravitational potential of the inner
binary. The hydrodynamics, in particular the interaction with the gas,
in turn affects the orbits of the two inner stars. With
\texttt{Bridge} we realize a second order coupling between the
gravitational dynamics and the hydrodynamics.  The interval at which
the gravity and hydrodynamics interact via \texttt{Bridge} depends on
the parameters of the system we study, but typically we achieve
converged solutions when this time step is about a fraction of 1/100
of the inner binary orbital period.

++++

@@

We adopt initial component masses of $m_{\rm 1} = 1.1$ M$_{\rm \odot}$
and $m_{\rm 2} = 0.9$ M$_{\rm \odot}$ for the inner binary components,
and $m_{\rm 3} = 1.2$ M$_{\rm \odot}$ for the tertiary star.  We
evolve the 1.2\,\MSun\, star using the MESA stellar evolution code
\cite{2011ApJS..192....3P} to a radius of about 1\,au.  By this time
the star has lost 0.13\,\MSun\, via a stellar wind.  We turned the
stellar evolution model, structure and temperature composition, into a
smoothed-particles representation using the module {\tt
  StellarModelInSPH} in AMUSE (see chapter 4 in \cite{AMUSE}).  We
replace the stellar core by a point mass to precent that all the
resolution will be in the central portion of the star instead of the
envelope. In a following step we relax the star using the
hydrodynamics solver. This relaxation process is realized in 100 steps
during which we reduce the velocity dispersion of individual SPH
particles to a glasseas structure \citep[see, for example, \S\,3.3 on
  page 40 in][]{1994astro.ph.10043W}.

With these parameters the orbital separation of the outer binary
becomes 3.86\,au, and the mass loss has driven a slight eccentricity
deviating from an initially circular orbit to about 0.0082 at the
moment of Roche-lobe overflow. We choose a relative initial
inclination of $i = 9^\circ$ between the inner and the outer orbits,
since observed stellar triples composed of low-mass stars have been
observed to favor co-planar configurations \citep{moe18}.
%NL: What are the initial orbital separations?  Why this choice of initial inclination? - I added a sentence and reference to justify it.

@@

\begin{figure}[ht!]
  \includegraphics[width=\columnwidth]{fig_MvsTime_N80k_M012R100RSun1109MSun_a02au.pdf}
\caption{Evolution of the masses (normalized to those at the moment of
  RLOF) for each of the three stars in the simulated triple as a function of
  time for the first 1000\,days. (see fig.\,\ref{fig:topview_at_t0}
  for a face-on representation of the initial conditions and
  fig.\,\ref{fig:topview_at_t1000day} for the final conditions}.  The
green and orange dashed curves give the masses of the inner two stars,
whereas the solid blue curve is the mass of the outer most star.
\label{fig:mass_evolution_for_M1.2M1.1M0.9a02e00i09}
\end{figure}

The orbital evolution of the inner binary circumreferenced by a disk
tends to evove by the accretion of mass and angular momentum. As a
consequence, the two stars in the binary accumulate mass, and their
orbit shrinks. The orbital evolution can be approximated, to first order, by:
\begin{equation}
  d\ln a \over dt   = - d\ln m_{\rm in} \over dt,
\end{equation}
where $a$ and $m_{\rm in}$ are the semimajor-axis and total mass in
the inner binary.  In the simulations we measure ${\dln a \over dt}
\simeq -0.0843$\,Myr$^{-1}$.

@@

\item The BSs in the inner binary should have roughly equal masses,
  independent of their initial masses.  This is because it is the
  lowest mass object that typically accretes the fastest, since its
  orbital velocity and distance relative to the circumbinary disk is
  typically the lowest
  \citep[e.g.][]{kroupa95,bate97,bate00,haiman09,bate12,farris15,rafikov16,kelley17}.
  This quickly brings the mass ratio toward unity.  This predicts that
  the initially lower mass MS star should accrete the most, and should
  hence be enriched more by any accreted material.  This could be
  observable in the surface layers of a radiative star.  If the donor
  is an RGB star, the accretor will be enriched in mostly carbon,
  oxygen and helium.  If the donor is an AGB star, it will be enriched
  in mostly s-process elements.
